%% -*- coding: utf-8; -*-

% Use 'digital' option to enable back references. This option is recommended for digital pdf version
%\documentclass[phd,american,digital]{thesispuc}%english thesis
%\documentclass[mscr,american]{thesispuc}%english dissertation
%\documentclass[phd,brazilian]{thesispuc}%tese em portugês
\documentclass[msc,brazilian]{thesispuc}%disseretação em portuguŝ


%%%
%%% Additional Packages
%%%
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage[%
    dvipsnames,
    svgnames,
    x11names,
    fixpdftex,
    table
]{xcolor}
\usepackage{numprint}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{amssymb}
% ABNT reference style package. The current style is the alphabetical order, if you need
% change to citation order, change in the line above 'alf' to 'num', also at the end replace
% bibliographystyle with the commented version.
\usepackage[num]{abntex2cite}
%\usepackage{tikz}
%\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
%\usepackage{pgfplots,pgfplotstable} 
%\usepackage{array}

% ADICIONADAS POR DANIEL
\usepackage{multirow}
\usepackage{longtable}
\usepackage{mathtools}

%% numprint 
\npthousandsep{.}
\npdecimalsign{,}

%% ThesisPUC option
%\tablesmode{fig} %% [nada, fig, tab ou figtab]
%\algoritmsmode{none} %% [none ou use] %% Default is [use]
%\codesmode{none} %% [none ou use] %% Default is [use]
%\abreviationsmode{none} %% [none ou use] %% Default is [use]

\tablesmode{figtab}

\algorithmsmode{none}
\codesmode{use}
\abreviationsmode{none}

% \makeatletter  \renewcommand\@biblabel[1]{#1}  \makeatother

%%%
%%% Counters
%%%

%% uncomment and change for other depth values
\setcounter{tocdepth}{1}
%\setcounter{lofdepth}{3}
%\setcounter{lotdepth}{3}
%\setcounter{secnumdepth}{3}

%%%
%%% Misc.
%%%

\usecolour{true}
%% \graphicspath{ {./figuras/} }
%% https://www.overleaf.com/learn/latex/Inserting_Images
\citebrackets[]

\renewcommand{\arraystretch}{1.5}


%%%
%%% Titulos
%%%

\autor{Daniel Schreiber Guimarães}
\autorR{Guimarães, Daniel Schreiber}

\advisor{Marcos Vianna Villas}{Prof.}
\advisorR{Villas, Marcos Vianna}
% If the advisor's department is different from author's department, uncomment the next line and type the correct name and acronym of advisor's institution.
%\advisorInst{institution name}{acronym}

%\coadvisor{Otávio da Fonseca Martins Gomes}{Dr.}
%\coadvisorR{da Fonseca Martins Gomes, Otávio}
%\coadvisorInst{Centro de Tecnologia Mineral}{CETEM/MCTI}

\title{Sistema de recomendação de disciplinas para matrícula de um aluno da PUC-Rio}
\titleuk{Course recommendation system for the enrolling of a PUC-Rio student}

%%\subtitulo{Aqui vai o subtitulo caso precise}

\day{24}
\month{Novembro}
\year{2023}

\city{Rio de Janeiro}
\CDD{004} 
\department{Informática}
\program{\mbox{Engenharia} da \mbox{Computação}}
\school{\mbox{Engenharia} da \mbox{Computação}}
\university{Pontifícia Universidade Católica do Rio de Janeiro}
\uni{PUC-Rio}


%%%
%%% Jury
%%%

\jury{%
  \jurymember{Sérgio Lifschitz}{Prof.}
    {Departamento de Informática}{PUC-Rio}
  \jurymember{Augusto Baffa}{Prof.}
    {Departamento de Informática}{PUC-Rio}
}


%%%
%%% Personal Resume
%%%

\resume{%
% If it fit in one line use this command:
\makebox[\textwidth][s]{Graduando em Engenharia da Computação na PUC - Rio}%
% If not just type your resume without any special command 
}

%%%
%%% Acknowledgment (REMINDER TO SCHOLARSHIP STUDENTS. Do not forget to thank the agencies that supported your work.)
%%% REMOVIDO POR DANIEL
%%%
% \acknowledgment{%
% \noindent To my adviser Professor Marcelo Gattass for the stimulus and partnership
% to carry out this work.
% \bigskip

% \noindent To CNPq and PUC-Rio, for the aids granted, without which this work does not
% could have been accomplished.
% \bigskip
% }


%%%
%%% Catalog prekeywords
%%%

\catalogprekeywords{%
  \catalogprekey{Informática}%
}

%%%
%%% Keywords - Don't use % at the end of /key dfinition
%%%

\keywords{%
  \key{Recomendação}
  \key{Disciplinas}
  \key{Algoritmo}
}

\keywordsuk{%
  \key{Recommendation}
  \key{Courses}
  \key{Algorithm}
}


%%%
%%% Abstract
%%%

\abstract{%
A PUC-Rio permite que os alunos escolham quais disciplinas irão cursar no próximo semestre, mas a tomada de decisão não é uma tarefa fácil, visto que as informações
relevantes como dificuldade da matéria, horários disponíveis ou professores disponíveis não são triviais de se encontrar. Esse projeto de graduação é referente
a um sistema que oferece uma plataforma para alunos montarem suas grades, avaliarem disciplinas e professores, e receberem recomendações de disciplinas para serem
cursadas.
} 

\abstractuk{%
PUC-Rio allows students to choose which courses they may take in the next semester, but decision-making is not an easy task, given that relevant informação such 
as the difficulty of the subject, available schedules, or available professor is not trivial to find. This graduation project is related to a system that provides
a plataform for students to build their schedules, evaluate courses and professors, and receive recommendations for courses to be taken.
}


%%%
%%% Dedication
%%%

\dedication{%
  Para os meus pais, que\\nunca deixaram de me ajudar.
}

%%%
%%% Epigraph (removido manualmente pelo thesispuc.cls)
%%%

% \epigraph{%
% }
% \epigraphauthor{Wassily Kandinsky}
% \epigraphbook{Regards sur le passé}


\begin{document}
  \input{conteudo/1-introducao}
  \input{conteudo/2-situacao-atual}
  \input{conteudo/3-objetivo-proposta}
  \input{conteudo/4-plano-acao}
  \input{conteudo/5-validacao-problema}
  \input{conteudo/6-requisitos}
  \input{conteudo/7-casos-uso}
  \input{conteudo/8-wireframes}
  \input{conteudo/9-dados}
  \input{conteudo/10-construcao}
  \input{conteudo/11-testes}
  \input{conteudo/12-uso-real}
  \input{conteudo/13-conclusao}
  
  \arial
  \bibliographystyle{abnt-num} % \bibliographystyle{abnt-alf}
  \bibliography{main} 
\end{document}
